Reliable error estimation for Sobol' indices

### 2016-03-11 replicated_sobol.tex
Adding more changes to Sobol background in replicated Sobol article

In this section we introduce a particular type of quasi-Monte Carlo points to estimate $\eqref{first_order_indice}$, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{2^m}$ only one time to estimate all $d$ indices.

@@

\subsection{Replicated Digital Sequences}
Here recall the link with the replicated method....
\begin{defin}
A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the replicated digital sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
\end{defin}
In this case, $C_j'$ will depend on the choice of $C_j$.

@@

Considering the generating matrices to be upper triangular and without zeros on the diagonal, one ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$. Since the block $C_j^{m\times m}$ is full rank, each $x_{i,j}\neq x_{r,j}$ when $i\neq j$. Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimension. When $b=2$, this is the case of Sobol' sequences and one could simply consider $C_{j+d},\dots,C_{2d}$ to generate the replicated sequence.

Because we are estimating the integral \eqref{first_order_indice}, we want to minimize the t-value of the following $d$ sequences at the same time............

According to \eqref{first_order_indice}, our dimension of study is $s = 2d-1$.

$X$,$X'$ are two sequences such that,
\[
X = \begin{pmatrix}
x_1^1,\dots,x_1^d \\
x_2^1,\dots,x_2^d \\
x_3^1,\dots,x_3^d \\
\end{pmatrix} \\
X' = \begin{pmatrix}
\pi_1(x_1^1),\dots,\pi_d(x_1^d) \\
\pi_1(x_2^1),\dots,\pi_d(x_2^d) \\
\pi_1(x_3^1),\dots,\pi_d(x_3^d) \\
\end{pmatrix}
\]

These sequences can be generated indeed with Owen scramblings, or which is equivalent, matrix generators $C_i$

@@

Not all choices are possible, for instance order 2 and higher Sobol' indices.

@@

>>>>

In this section we introduce a particular type of quasi-Monte Carlo points to estimate $\eqref{first_order_indice}$, which will allow us to evaluate the integrand at points $\{\left(\vx_i,{\vx'}_{i,-u}\right)\}_{i=0}^{b^m}$ only one time to estimate all $d$ indices.

@@

\subsection{Replicated Digital Sequences}
Here recall the link with the replicated method....
\begin{defin}
A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the \emph{replicated digital} sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
\end{defin}
In this case, $C_j'$ will depend on the choice of $C_j$.

If we do higher order Sobol' indices, we can easily show that $C'_{i}=AC_{i}$ for $i = 1,\dots,d$, and this does not work because this means having the same function values for each $u$, with a unique ordering given by $A$.

@@

For this special case, we consider the generating matrices to be upper triangular. This ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$. If we also assume that there are no zeros on the diagonal, the block $C_j^{m\times m}$ is full rank and each $x_{i,j}\neq x_{r,j}$ when $i\neq r$. Therefore, excluding the trivial case, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimensions to obtain a \emph{replicated digital sequence}. When $b=2$, these are Sobol' sequences.

For quasi-Monte Carlo integration purposes, given $\{{\vx}_i\}_{i\in\mathbb{N}_0}$ generated by $C_{1},\dots,C_{d}$, and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ generated by $C'_{1},\dots,C'_{d}$, the $d$ sequences in dimension $2d-1$ used to estimate all $\underline{\tau}_u^2$ are generated by
\begin{equation}\label{ordered_sequence}
\underbrace{C_{1},\dots,C_{d}}_{\text{First }d\text{ dimensions}},\underbrace{C_{\alpha(u,1)},\dots,C_{\alpha(u,u-1)},C_{\alpha(u,u+1)},\dots,C_{\alpha(u,d)}}_{\text{Next }d-1\text{ dimensions}},\quad 1\leq u \leq d\, ,
\end{equation}
where $C_{\alpha(u,i)}:=C_u(C'_{u})^{-1}C'_{i}$. Note that for $i=u$, one has $C_{\alpha(u,u)}=C_u$. This is in fact forcing $C_u = C'_{u}$, as desired to apply the replicated method. Therefore, our goal is to find a good choice of $C_{1},\dots,C_{d},C'_{1},\dots,C'_{d}$ such that for all $u=1,\dots,d$, the sequence used to estimate $\underline{\tau}_u^2$ has a low $t$-value.

The best choice of primitive polynomials and directional numbers to generate good quality Sobol' sequences is deeply discussed in \cite{•}. We are going to take Kuo and Joe results to find  good \emph{replicated Sobol'} sequences.

Pairwise projections are already well optimized (see\cite[Table 2.1]{•}). Thus, our starting point will be using the $C_1,\dots,C_d$ found in \cite{•} to generate the sequence $\{{\vx}_i\}_{i\in\mathbb{N}_0}$. Hence, we will focus on finding the optimal $C'_{1},\dots,C'_{d}$ such that we minimize a $t$-value criteria (to specify, perhaps the max of all) over all $d$ sequences described in \eqref{ordered_sequence}.

@@

@@

It will be easy to write that we can apply an Owen scrambling to each dimension separately, and we only need to keep the same scrambling for $C_j$ and $C'_j$.
